---
title: "Week4Assignment"
author: "Joseph Ellinghaus"
date: "September 26, 2014"
output: pdf_document
---

Which year were the best popular movies made?

The definition of "best popular" will be defined as the movies that were at least
60 minutes long, received ratings by IMDB voting > 9.5 and were mpaa rated  < PG,
i.e. not rated PG, PG-13, R, or NC-17. The year the best popular movies were made
will be defined as the year with the most movies meeting the "best popular" criteria.

The best popular movies were made in 2004.

```{r}
library(ggplot2)
library(dplyr)

m <- read.table("movies.tab", sep="\t", header=TRUE, quote="", comment="")
(movies_df <- tbl_df(m))  # read in data and create wrapper
(bp1 <- arrange(movies_df, desc(rating))) # sort by rating descending
(bp2 <- select(bp1, year, title, rating, length)) # include year, title, rating, and length
(bp3 <- filter(bp2, length >= 60, rating >9.5))  # filter by the "best popular" criteria
(bp4 <- group_by(bp3, year))  # group by year to identify highest frequency
(bp5 <- summarize(bp4,
                  count=n()))  # summarize for plotting
(bp6 <- arrange(bp5, desc(count)))  # sort for best display
(bp7 <- bp6[1:5,])  # include the top five years for the graph
```

Embeded plot:

```{r, echo=FALSE}
(BestPopularMovies <- ggplot(bp7, aes(x=factor(year), y=count)) +
   geom_bar(stat="identity"))
```
